An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-17 indicators/paper/paper.tex
Temp commit so I can pull

Since July 2020, Delphi has been regularly submitting short-term forecasts of
COVID-19 case and death incidence, at the state and county levels, to the
COVID-19 Forecast Hub \cite{ForecastHub}, under the name ``CMU-TimeSeries''.  
The process of building, training, and deploying our forecasting models
leverages much of the infrastructure described in this paper (such as the
COVIDcast API's \textit{as of} feature), and some of our forecasting systems
rely on auxiliary indicators (such as survey-based and claims-based COVID-like 
illness signals, described below, which we have used in case forecasting).

>>>>

Since July 2020, Delphi has been regularly submitting short-term forecasts of
COVID-19 case and death incidence, at the state and county levels, to the
COVID-19 Forecast Hub \cite{ForecastHub}, with ``CMU-TimeSeries'' as the
team-model name.  The process of building, training, and deploying our
forecasting models leverages much of the infrastructure described in this paper
(such as the COVIDcast API's \textit{as of} feature), and some of our
forecasting systems rely on auxiliary indicators (such as survey-based and
claims-based COVID-like illness signals, which are described below).
